---
title: "Dissertation main script"
author: "Wangjingyi Liao c21102271"
date: "23/08/2022"
output:
  html_document:
    df_print: paged
---

```{r}
options(knitr.duplicate.label = "allow")

library(tidyverse)
library(ggplot2)
library(naniar)
library(survival)
library(survminer)
library(flextable)
library(ggpubr)
library(gtsummary)
library(webshot2)

source_rmd = function(file, ...) {
  tmp_file = tempfile(fileext=".R")
  on.exit(unlink(tmp_file), add = TRUE)
  knitr::purl(file, output=tmp_file)
  source(file = tmp_file, ...)
}



```
### Read in the phenotype files 
```{R}

phenotypeData <- read_table('../Data/BG_Trio_phenotypes.txt', col_names = T, col_types = 'cnnnnnnnnnn')


phenotypeData2 <- read_table('../Data/BG_trios_YOB_blood.tsv', col_names = T)


phenotypeData <- merge(phenotypeData,phenotypeData2)
phenotypeData$age <- phenotypeData$blood_year - phenotypeData$Yearofbirth

phenotypeData <- phenotypeData %>% relocate(SampleID, Yearofbirth, blood_year, age,everything())

```


### Remove the siblings data, keep only the proband and their parents, and remove the unkown sex individual
```{r}

phenotypeData2 <- phenotypeData %>% separate(SampleID, c('FamilyID', 'IndividualID')) 

phenotypeData2[['IndividualID']] <- as.numeric(phenotypeData2[['IndividualID']])

phenotypeData3 <- phenotypeData2 %>% filter(IndividualID ==1 | IndividualID==2 |IndividualID == 3) %>% filter(sex == 1 | sex == 2)

phenotypeData3[['IID']] <- str_c(phenotypeData3$FamilyID, '-', phenotypeData3$IndividualID)

phenotypeData3[['IndividualID']] <- as.character(phenotypeData3[['IndividualID']])

phenotypeData_for_PRSice <- phenotypeData3 %>% dplyr::select(FamilyID)

write.table(phenotypeData_for_PRSice, '../Data/PostQC.pheno', quote = F, row.names = F)





```

### identify the non-european sample 
```{r}

PC <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/PCA/Trios_PCA1.eigenvec', col_names = F)
PC <- PC[, 2:12]
colnames(PC) <- c('IID','PC1', 'PC2', 'PC3', 'PC4', 'PC5', 'PC6', 'PC7', 'PC8', 'PC9', 'PC10')
PC <- PC %>% separate(IID, c('FamilyID', 'IndividualID')) 

PC[['FamilyID']] <- as.character(PC[['FamilyID']])

source_rmd('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Script/removing_PCA_outliners.Rmd')
```

### Merge the PRS results with the phenotype and PCs

```{r}
phenotype_pc <- left_join(PC,phenotypeData3)

SCZ_PRS <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/SZC PGS/SCZ_polygenic.all_score')
SCZ_PRS[['FID']] <- as.character(SCZ_PRS[['FID']])
colnames(SCZ_PRS) <- c('FamilyID', 'IID', 'SCZ_Pt_0.001', 'SCZ_Pt_0.05', 'SCZ_Pt_0.5','SCZ_Pt_1')
phenotype_pc_prs <- left_join(phenotype_pc, SCZ_PRS)

BD_PRS <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/Biopolar PGS/BD_polygenic.all_score')
BD_PRS[['FID']] <- as.character(BD_PRS[['FID']])
colnames(BD_PRS) <- c("FamilyID", "IID", "BD_Pt_0.001", "BD_Pt_0.05", "BD_Pt_0.5", "BD_Pt_1")
phenotype_pc_prs <- left_join(phenotype_pc_prs, BD_PRS)

MDD_PRS <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/MDD PGS/MDD_PGS.all_score')
MDD_PRS[['FID']] <- as.character(MDD_PRS[['FID']])
colnames(MDD_PRS) <- c("FamilyID", "IID", "MDD_Pt_0.001", "MDD_Pt_0.05", "MDD_Pt_0.5", "MDD_Pt_1")
phenotype_pc_prs <- left_join(phenotype_pc_prs, MDD_PRS)

IQ_PRS <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/IQ PGS/iq_polygenic.all_score')
IQ_PRS[['FID']] <- as.character(IQ_PRS[['FID']])
colnames(IQ_PRS) <- c("FamilyID", "IID", "IQ_Pt_0.001", "IQ_Pt_0.05", "IQ_Pt_0.5", "IQ_Pt_1")
phenotype_pc_prs <- left_join(phenotype_pc_prs, IQ_PRS)


EF_PRS <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/EF PGS/EF_PGS.all_score')
EF_PRS[['FID']] <- as.character(EF_PRS[['FID']])
colnames(EF_PRS) <- c("FamilyID", "IID", "EF_Pt_0.001", "EF_Pt_0.05", "EF_Pt_0.5", "EF_Pt_1")
phenotype_pc_prs <- left_join(phenotype_pc_prs, EF_PRS)

CUD_PRS <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/CUD PGS/CUD_polygenic.all_score')
CUD_PRS[['FID']] <- as.character(CUD_PRS[['FID']])
colnames(CUD_PRS) <- c("FamilyID", "IID", "CUD_Pt_0.001", "CUD_Pt_0.05", "CUD_Pt_0.5", "CUD_Pt_1")
phenotype_pc_prs <- left_join(phenotype_pc_prs, CUD_PRS)

alcohol_PRS <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/Alcohol Dependence PGS/alcohol_dep_pgs.all_score')
alcohol_PRS[['FID']] <- as.character(alcohol_PRS[['FID']])
colnames(alcohol_PRS) <- c("FamilyID", "IID", "alcohol_Pt_0.001", "alcohol_Pt_0.05", "alcohol_Pt_0.5", "alcohol_Pt_1")
phenotype_pc_prs <- left_join(phenotype_pc_prs, alcohol_PRS)

Smoking_PRS <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/Smoking PGS/smoking_PGS.all_score')
Smoking_PRS[['FID']] <- as.character(Smoking_PRS[['FID']])
colnames(Smoking_PRS) <- c("FamilyID", "IID", "smoking_Pt_0.001", "smoking_Pt_0.05", "smoking_Pt_0.5", "smoking_Pt_1")
phenotype_pc_prs <- left_join(phenotype_pc_prs, Smoking_PRS)

phenotype_pc_prs <- phenotype_pc_prs %>% 
  mutate_at(c('SCZ_Pt_0.001', 'SCZ_Pt_0.05', 'SCZ_Pt_0.5','SCZ_Pt_1', 
              "BD_Pt_0.001", "BD_Pt_0.05", "BD_Pt_0.5", "BD_Pt_1",
              "MDD_Pt_0.001", "MDD_Pt_0.05", "MDD_Pt_0.5", "MDD_Pt_1",
              "IQ_Pt_0.001", "IQ_Pt_0.05", "IQ_Pt_0.5", "IQ_Pt_1", 
              "EF_Pt_0.001", "EF_Pt_0.05", "EF_Pt_0.5", "EF_Pt_1", 
              "CUD_Pt_0.001", "CUD_Pt_0.05", "CUD_Pt_0.5", "CUD_Pt_1",
              "alcohol_Pt_0.001", "alcohol_Pt_0.05", "alcohol_Pt_0.5", "alcohol_Pt_1",
              "smoking_Pt_0.001", "smoking_Pt_0.05", "smoking_Pt_0.5", "smoking_Pt_1"), ~(scale(.) %>% as.vector))


```

### read-in Durations_of_illness variable 
```{r}
Durations_of_illness<- read.table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/BG_Illness_duration.txt', header = T, sep = '\t', na.strings = " ") %>% dplyr::select(-age)
phenotype_pc_prs <- left_join(phenotype_pc_prs, Durations_of_illness, by = c('IID' = 'SampleID',"sex", "ill_onset_imp", "first_hosp", "num_hosp"))

```
### read_in family history and create new binary variable
```{r}
family_history <- read.table('../Data/BG_trios_fh.txt', head = T, sep = '\t')

family_history$fam_hist_proximity %>% table(useNA='always')
#2 = close family (parents/sibling)
#1 = distal family (cousins, grandparents)
#0 = no family history (donot have or dont know)
family_history$fam_hist_psychosis %>% table(useNA='always')
#2 = psychosis
#1 = other mental disease
#0 = no family history

family_history <- family_history %>% mutate(family_history = case_when(fam_hist_proximity >0 & fam_hist_psychosis > 0 ~ 1, fam_hist_proximity == 0 & fam_hist_psychosis == 0 ~ 0))

phenotype_pc_prs  <- left_join(phenotype_pc_prs, family_history, by = c('IID' = 'SampleID'))

phenotype_pc_prs$family_history %>% table(useNA='always')

```




### create the ntPRS and pTDT

```{R}
source_rmd('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Script/Non-transmitted PRS.Rmd')
```

### limite the data to cases only, DSM2&3 and duration <5
```{r}
case_phenotype_prs <- phenotype_pc_prs %>% 
  filter(IndividualID == 1) %>% 
  filter(DSM4 ==3)%>%
  filter(!(FamilyID %in% excluding_family_id))

case_phenotype_prs <- case_phenotype_prs %>% replace_with_na(replace = list(quality_remissions = 0)) %>% 
  replace_with_na(replace = list(first_hosp = 0)) %>% 
  replace_with_na(replace = list(num_hosp = 0))

case_phenotype_prs <- case_phenotype_prs %>% dplyr::select(FamilyID, IndividualID, IID,Yearofbirth,blood_year, age,  ill_onset_imp, first_hosp, num_hosp, first_psy,Durations_of_illness, quality_remissions,place_of_birth,family_history,DSM4, sex,everything())

```




### create survival objects
```{r}

case_phenotype_prs$status <- 1

surv_object_illonset <- Surv(case_phenotype_prs$ill_onset_imp, case_phenotype_prs$status)
fit1 <- survfit(surv_object_illonset ~ 1, data = case_phenotype_prs)
ggsurvplot(fit1,data = case_phenotype_prs, pval = T)

#surv_object_first_hosp <- Surv(case_phenotype_prs$first_hosp, case_phenotype_prs$status)
#fit2 <- survfit(surv_object_first_hosp ~ 1, data = case_phenotype_prs)
#ggsurvplot(fit2,data = case_phenotype_prs, pval = T)

```

### change the classes of data
```{r}

library(MASS)

case_phenotype_prs$quality_remissions <- as.factor(case_phenotype_prs$quality_remissions)
case_phenotype_prs$place_of_birth_num <- as.factor(case_phenotype_prs$place_of_birth)

```
```{r}
library(stringr)
```

#### results

### number of hosp PRS
```{r}

num_hosp_prsmod <- list()
num_hosp_prstable <- data.frame()
for(i in 1:8){
  predictors_covariables <- c('sex', 'age', 'Durations_of_illness','PC1', 'PC2' , 'PC3', 'PC4','PC5', 'PC6' , 'PC7', 'PC8','PC9','PC10')
  predictors_prs <- str_subset(colnames(case_phenotype_prs),'_0.05')[i:i] 
  predictors <- predictors_prs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_prsmod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_prsmod[[i]])
  confint <- confint(num_hosp_prsmod[[i]])
  num_hosp_prstable <- data.frame(PRS=rownames(summary$coefficients)[2], Estimate = summary$coefficients[predictors_prs,'Estimate'],RateRatio = exp(summary$coefficients[predictors_prs,'Estimate']), CI_lower = exp(confint[predictors_prs, '2.5 %']), CI_upper = exp(confint[predictors_prs, '97.5 %']), pvalue=summary$coefficients[predictors_prs,'Pr(>|z|)']) %>% add_row(num_hosp_prstable,.before = 1)
}

#explantiohn use odd ratio to make esier interprettion
p.adjust(num_hosp_prstable$pvalue, method='bonferroni', n = 24)

num_hosp_prstable <- num_hosp_prstable %>% mutate(sign = case_when(pvalue < 0.05 ~ 'Significant at p = 0.05', pvalue > 0.05 ~ 'Not significant'))

num_hosp_prstable<- num_hosp_prstable %>% mutate(PRS = str_replace(PRS,'SCZ_Pt_0.05', 'Schizophrenia'),PRS = str_replace(PRS,'BD_Pt_0.05', 'Bipolar Disorder'), PRS = str_replace(PRS,'MDD_Pt_0.05', 'Depression'), PRS = str_replace(PRS,'IQ_Pt_0.05', 'IQ'), PRS = str_replace(PRS,'EF_Pt_0.05', 'Executive Function'), PRS = str_replace(PRS,'CUD_Pt_0.05', 'Cannabis Use'), PRS = str_replace(PRS,'alcohol_Pt_0.05', 'Alcohol Dependence'),PRS = str_replace(PRS,'smoking_Pt_0.05', 'Smoking'))
                                                  
num_hosp_prstable_word <- mutate_if(num_hosp_prstable, is.numeric, round, digit = 3) 

num_hosp_prstable_word <- flextable(num_hosp_prstable_word, col_keys = c('PRS', 'Estimate', 'RateRatioCL', 'pvalue')) %>% 
  compose(j = 'RateRatioCL', value = as_paragraph(sprintf(RateRatio,fmt = '%#.3f '), as_bracket(CI_lower, CI_upper))) %>% 
  add_header_lines('Table  x: Proband PRS and Number of Hospitalization') %>% 
  color(~ pvalue < 0.001, ~ pvalue, color = "red") %>% 
  set_header_labels(values = list(
  Estimate = 'Beta',
  pvalue = 'P value',
  RateRatioCL = 'Rate Ratio (95% CI)'
))%>% 
  set_table_properties(layout = "autofit") 

# BD passed multiple comparision problems
#analysis for pTDT
pTDT_bd_for_num_hosp  <- glm(num_hosp ~ pTDT_bd + sex + age + Durations_of_illness,data = case_phenotype_prs, family = poisson)

summary(pTDT_bd_for_num_hosp)

confint(pTDT_bd_for_num_hosp)

```

### number of hosp ntPRS
```{R}
num_hosp_ntprsmod <- list()
num_hosp_ntprstable <- data.frame()
for(i in 1:8){
  predictors_covariables <- c('sex', 'age', 'Durations_of_illness','PC1', 'PC2' , 'PC3', 'PC4','PC5', 'PC6' , 'PC7', 'PC8','PC9','PC10')
  predictors_ntprs <- str_subset(colnames(case_phenotype_prs),'non_transmitted')[i:i] 
  predictors <- predictors_ntprs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_ntprsmod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_ntprsmod[[i]])
  confint <- confint(num_hosp_ntprsmod[[i]])
  num_hosp_ntprstable <- data.frame(ntPRS=rownames(summary$coefficients)[2],  Estimate = summary$coefficients[predictors_ntprs,'Estimate'], RateRatio = exp(summary$coefficients[predictors_ntprs,'Estimate']), CI_lower = exp(confint[predictors_ntprs, '2.5 %']), CI_upper = exp(confint[predictors_ntprs, '97.5 %']), pvalue =summary$coefficients[predictors_ntprs,'Pr(>|z|)']) %>% add_row(num_hosp_ntprstable,.before = 1)
}
p.adjust(num_hosp_ntprstable$'pvalue', method='bonferroni', n = 24)

num_hosp_ntprstable <- num_hosp_ntprstable %>% mutate(sign = case_when(pvalue < 0.05 ~ 'Significant at p = 0.05', pvalue > 0.05 ~ 'Not significant'))

#IQ, EF and Smoking passed the correction

num_hosp_ntprstable <- num_hosp_ntprstable %>% mutate(ntPRS = str_replace(ntPRS,'non_transmitted_prs_scz', 'Schizophrenia'),ntPRS = str_replace(ntPRS,'non_transmitted_prs_bd', 'Bipolar Disorder'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_mdd', 'Depression'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_IQ', 'IQ'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_EF', 'Executive Function'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_cud', 'Cannabis Use'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_alcohol', 'Alcohol Dependence'),ntPRS = str_replace(ntPRS,'non_transmitted_prs_smoking', 'Smoking'))

num_hosp_ntprstable_word <- mutate_if(num_hosp_ntprstable, is.numeric, round, digit = 3)

num_hosp_ntprstable_word <- flextable(num_hosp_ntprstable_word, col_keys = c('ntPRS', 'Estimate', 'RateRatioCL', 'pvalue')) %>% 
  compose(j = 'RateRatioCL', value = as_paragraph(sprintf(RateRatio,fmt = '%#.3f '), as_bracket(CI_lower, CI_upper))) %>% 
  add_header_lines('Table  x: Proband ntPRS and Number of Hospitalization') %>% 
  color(~ pvalue < 0.001, ~ pvalue, color = "red") %>% 
  set_header_labels(values = list(
  Estimate = 'Beta',
  ntPRS = 'ntPGS',
  pvalue = 'P value',
  RateRatioCL = 'Rate Ratio (95% CI)'
)) %>% set_table_properties(layout = "autofit") 
```

```{r}
num_hosp_prstable
num_hosp_ntprstable

num_hosp_prstable$type <- 'PGS'
num_hosp_ntprstable$type <- 'ntPGS'

colnames(num_hosp_prstable)[1] <- 'PGS'
colnames(num_hosp_ntprstable)[1] <- 'PGS'


test <- rbind(num_hosp_prstable, num_hosp_ntprstable)

test$type <- as.factor(test$type) %>% relevel('PGS')
test$PGS <- as.factor(test$PGS) %>% ordered(levels = rev(c('Schizophrenia',"Bipolar Disorder","Depression","IQ","Executive Function","Cannabis Use","Alcohol Dependence","Smoking")))


ggplot(test, aes(y = PGS, x = RateRatio)) +
  geom_point(aes(color = sign),shape = 18, size = 5) +  
  scale_color_manual(values = c("black", 'pink'), name = '') + 
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper), height = 0.25) +
  geom_vline(xintercept = 1, color = "red", linetype = "dashed", cex = 1, alpha = 0.5) + facet_wrap(~type)+
  xlab("Rate Ratio (95% CI)") + 
  ylab(" ") + theme_classic() +
  ggtitle('Figure 13: PGS and ntPGS with number of hospitalizations (SA)') +
  theme(plot.title = element_text(hjust = 0.4))

ggsave(filename = 'figure13_prs_ntprs_num_hosp_sa.tiff', units = 'in', width = 7.5, height = 5, dpi = 700, device = 'tiff')

table11 <- as_grouped_data(x = test, groups = c('type')) %>% flextable::as_flextable(col_keys = c('Genotype', 'RRCI', 'pvalue'))%>% 
  compose(j = 'RRCI', i= ~ is.na(type), value = as_paragraph(sprintf(RateRatio,fmt = '%#.3f '), as_bracket(CI_lower, CI_upper))) %>%compose(j = 'Genotype',i= ~ is.na(type), value = as_paragraph(PGS)) %>%
  compose(j = 'pvalue', i= ~ is.na(type), value = as_paragraph(sprintf(pvalue,fmt = '%#.3f '))) %>%
  add_header_lines('Table  11: Proband PGS, ntPGS and number of hospitalizations in Schizoaffective cohort') %>% 
  color(~ pvalue < 0.05, ~ pvalue, color = "red") %>% 
  set_header_labels(values = list(
  pvalue = 'P value',
  RRCI = 'Rate Ratio (95% CI)'
)) %>% bold(j = 1, i = ~ !is.na(type), bold = TRUE, part = "body") %>%
  bold(part = "header", bold = TRUE)%>% set_table_properties(layout = "autofit")

table11 %>%save_as_image(path = 'table11.png')

```


```{r}
#library(webshot)
#save_as_docx(num_hosp_prstable_word,num_hosp_ntprstable_word, path = 'dissertation table.docx')

#save_as_image(num_hosp_prstable_word,path = 'table7.png')
#save_as_image(num_hosp_ntprstable_word,path = 'table8.png')
```


