---
title: "Dissertation main script"
author: "Wangjingyi Liao c21102271"
date: "23/08/2022"
output:
  html_document:
    df_print: paged
---

```{r}
options(knitr.duplicate.label = "allow")

library(tidyverse)
library(ggplot2)
library(naniar)
library(survival)
library(survminer)
library(flextable)
library(ggpubr)
library(gtsummary)
library(webshot2)
source_rmd = function(file, ...) {
  tmp_file = tempfile(fileext=".R")
  on.exit(unlink(tmp_file), add = TRUE)
  knitr::purl(file, output=tmp_file)
  source(file = tmp_file, ...)
}



```
### Read in the phenotype files 
```{R}

phenotypeData <- read_table('../Data/BG_Trio_phenotypes.txt', col_names = T, col_types = 'cnnnnnnnnnn')


phenotypeData2 <- read_table('../Data/BG_trios_YOB_blood.tsv', col_names = T)


phenotypeData <- merge(phenotypeData,phenotypeData2)
phenotypeData$age <- phenotypeData$blood_year - phenotypeData$Yearofbirth

phenotypeData <- phenotypeData %>% relocate(SampleID, Yearofbirth, blood_year, age,everything())

```


### Remove the siblings data, keep only the proband and their parents, and remove the unkown sex individual
```{r}

phenotypeData2 <- phenotypeData %>% separate(SampleID, c('FamilyID', 'IndividualID')) 

phenotypeData2[['IndividualID']] <- as.numeric(phenotypeData2[['IndividualID']])

phenotypeData3 <- phenotypeData2 %>% filter(IndividualID ==1 | IndividualID==2 |IndividualID == 3) %>% filter(sex == 1 | sex == 2)

phenotypeData3[['IID']] <- str_c(phenotypeData3$FamilyID, '-', phenotypeData3$IndividualID)

phenotypeData3[['IndividualID']] <- as.character(phenotypeData3[['IndividualID']])

phenotypeData_for_PRSice <- phenotypeData3 %>% dplyr::select(FamilyID)

write.table(phenotypeData_for_PRSice, '../Data/PostQC.pheno', quote = F, row.names = F)


```

### Use pathfinder to covert the GWAS format

e.g. Rscript summaRygwasqc.V1.3.5.R --GWAS CUD_EUR_casecontrol_public_11.14.2020 --HRC HRC.Chr --PRS F --mthres 0.01 --ithres 0.8 --MHC T


### Use PRSice to calcualte the PRS

FOR SCZ

Rscript /mnt/d/Key\ Tools/PRSice_win64/PRSice.R 
--prsice /mnt/d/Key\ Tools/PRSice_win64/PRSice_win64.exe 
--A1 A1 
--A2 A2 
--bar-levels 0.001,0.05,0.5 
--base daner_sz3_RyQC.txt  
--binary-target F 
--chr CHR 
--clump-kb 250 
--clump-p 1.000000 
--clump-r2 0.200000 
--fastscore 
--model add 
--out SCZ_polygenic 
--all-score 
--pheno-col sex 
--pheno-file PostQC.pheno 
--pvalue P 
--snp SNP 
--stat BETA 
--target Bulgarian.Trios.QC.ALL 
--thread 1


### identify the non-european sample 
```{r}

PC <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/PCA/Trios_PCA1.eigenvec', col_names = F)
PC <- PC[, 2:12]
colnames(PC) <- c('IID','PC1', 'PC2', 'PC3', 'PC4', 'PC5', 'PC6', 'PC7', 'PC8', 'PC9', 'PC10')
PC <- PC %>% separate(IID, c('FamilyID', 'IndividualID')) 

PC[['FamilyID']] <- as.character(PC[['FamilyID']])


source_rmd('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Script/removing_PCA_outliners.Rmd')

```

### Merge the PRS results with the phenotype and PCs

```{r}
phenotype_pc <- left_join(PC,phenotypeData3)


SCZ_PRS <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/SZC PGS/SCZ_polygenic.all_score')
SCZ_PRS[['FID']] <- as.character(SCZ_PRS[['FID']])
colnames(SCZ_PRS) <- c('FamilyID', 'IID', 'SCZ_Pt_0.001', 'SCZ_Pt_0.05', 'SCZ_Pt_0.5','SCZ_Pt_1')
phenotype_pc_prs <- left_join(phenotype_pc, SCZ_PRS)

BD_PRS <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/Biopolar PGS/BD_polygenic.all_score')
BD_PRS[['FID']] <- as.character(BD_PRS[['FID']])
colnames(BD_PRS) <- c("FamilyID", "IID", "BD_Pt_0.001", "BD_Pt_0.05", "BD_Pt_0.5", "BD_Pt_1")
phenotype_pc_prs <- left_join(phenotype_pc_prs, BD_PRS)

MDD_PRS <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/MDD PGS/MDD_PGS.all_score')
MDD_PRS[['FID']] <- as.character(MDD_PRS[['FID']])
colnames(MDD_PRS) <- c("FamilyID", "IID", "MDD_Pt_0.001", "MDD_Pt_0.05", "MDD_Pt_0.5", "MDD_Pt_1")
phenotype_pc_prs <- left_join(phenotype_pc_prs, MDD_PRS)

IQ_PRS <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/IQ PGS/iq_polygenic.all_score')
IQ_PRS[['FID']] <- as.character(IQ_PRS[['FID']])
colnames(IQ_PRS) <- c("FamilyID", "IID", "IQ_Pt_0.001", "IQ_Pt_0.05", "IQ_Pt_0.5", "IQ_Pt_1")
phenotype_pc_prs <- left_join(phenotype_pc_prs, IQ_PRS)


EF_PRS <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/EF PGS/EF_PGS.all_score')
EF_PRS[['FID']] <- as.character(EF_PRS[['FID']])
colnames(EF_PRS) <- c("FamilyID", "IID", "EF_Pt_0.001", "EF_Pt_0.05", "EF_Pt_0.5", "EF_Pt_1")
phenotype_pc_prs <- left_join(phenotype_pc_prs, EF_PRS)

CUD_PRS <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/CUD PGS/CUD_polygenic.all_score')
CUD_PRS[['FID']] <- as.character(CUD_PRS[['FID']])
colnames(CUD_PRS) <- c("FamilyID", "IID", "CUD_Pt_0.001", "CUD_Pt_0.05", "CUD_Pt_0.5", "CUD_Pt_1")
phenotype_pc_prs <- left_join(phenotype_pc_prs, CUD_PRS)

alcohol_PRS <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/Alcohol Dependence PGS/alcohol_dep_pgs.all_score')
alcohol_PRS[['FID']] <- as.character(alcohol_PRS[['FID']])
colnames(alcohol_PRS) <- c("FamilyID", "IID", "alcohol_Pt_0.001", "alcohol_Pt_0.05", "alcohol_Pt_0.5", "alcohol_Pt_1")
phenotype_pc_prs <- left_join(phenotype_pc_prs, alcohol_PRS)

Smoking_PRS <- read_table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/Smoking PGS/smoking_PGS.all_score')
Smoking_PRS[['FID']] <- as.character(Smoking_PRS[['FID']])
colnames(Smoking_PRS) <- c("FamilyID", "IID", "smoking_Pt_0.001", "smoking_Pt_0.05", "smoking_Pt_0.5", "smoking_Pt_1")
phenotype_pc_prs <- left_join(phenotype_pc_prs, Smoking_PRS)

phenotype_pc_prs <- phenotype_pc_prs %>% 
  mutate_at(c('SCZ_Pt_0.001', 'SCZ_Pt_0.05', 'SCZ_Pt_0.5','SCZ_Pt_1', 
              "BD_Pt_0.001", "BD_Pt_0.05", "BD_Pt_0.5", "BD_Pt_1",
              "MDD_Pt_0.001", "MDD_Pt_0.05", "MDD_Pt_0.5", "MDD_Pt_1",
              "IQ_Pt_0.001", "IQ_Pt_0.05", "IQ_Pt_0.5", "IQ_Pt_1", 
              "EF_Pt_0.001", "EF_Pt_0.05", "EF_Pt_0.5", "EF_Pt_1", 
              "CUD_Pt_0.001", "CUD_Pt_0.05", "CUD_Pt_0.5", "CUD_Pt_1",
              "alcohol_Pt_0.001", "alcohol_Pt_0.05", "alcohol_Pt_0.5", "alcohol_Pt_1",
              "smoking_Pt_0.001", "smoking_Pt_0.05", "smoking_Pt_0.5", "smoking_Pt_1"), ~(scale(.) %>% as.vector))


```

### read-in Durations_of_illness variable 
```{r}
Durations_of_illness<- read.table('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Data/BG_Illness_duration.txt', header = T, sep = '\t', na.strings = " ") %>% dplyr::select(-age)
phenotype_pc_prs <- left_join(phenotype_pc_prs, Durations_of_illness, by = c('IID' = 'SampleID',"sex", "ill_onset_imp", "first_hosp", "num_hosp"))

```
### read_in family history and create new binary variable
```{r}
family_history <- read.table('../Data/BG_trios_fh.txt', head = T, sep = '\t')

family_history$fam_hist_proximity %>% table(useNA='always')
#2 = close family (parents/sibling)
#1 = distal family (cousins, grandparents)
#0 = no family history (donot have or dont know)
family_history$fam_hist_psychosis %>% table(useNA='always')
#2 = psychosis
#1 = other mental disease
#0 = no family history

family_history <- family_history %>% mutate(family_history = case_when(fam_hist_proximity >0 & fam_hist_psychosis > 0 ~ 1, fam_hist_proximity == 0 & fam_hist_psychosis == 0 ~ 0))

phenotype_pc_prs  <- left_join(phenotype_pc_prs, family_history, by = c('IID' = 'SampleID'))

phenotype_pc_prs$family_history %>% table(useNA='always')

parent_psychosis <- family_history %>% mutate(parent_psychosis = case_when(fam_hist_proximity == 2 & fam_hist_psychosis ==2 ~ 1, fam_hist_proximity < 2 | fam_hist_psychosis < 2 ~ 0))

phenotype_pc_prs  <- left_join(phenotype_pc_prs, parent_psychosis[,c('SampleID', 'parent_psychosis')], by = c('IID' = 'SampleID'))

phenotype_pc_prs$parent_psychosis %>% table(useNA='always')

```




### create the ntPRS and pTDT

```{R}
source_rmd('D:/MSc Bioinformatics and genetic epidemology/Dissertation/Script/Non-transmitted PRS.Rmd')
```

### create a binary quality of remission variable

```{r}
phenotype_pc_prs <- phenotype_pc_prs %>% mutate(binary_quality_remission = case_when(quality_remissions == 1 ~ 1, quality_remissions > 1 ~ 0))


```

### limite the data to cases only, EU sample, DSM2&3 and duration <5
```{r}

case_phenotype_prs <- phenotype_pc_prs %>% 
  filter(IndividualID == 1) %>% 
  filter(DSM4 ==2 | DSM4 ==3) %>%
  filter(!(FamilyID %in% excluding_family_id))


case_phenotype_prs <- case_phenotype_prs %>% replace_with_na(replace = list(quality_remissions = 0)) %>% 
  replace_with_na(replace = list(first_hosp = 0)) %>% 
  replace_with_na(replace = list(num_hosp = 0))

```
### Range, mean, median, and missiness in the phenotypes. 
```{r}
#ggplot(case_phenotype_prs, aes(x = ill_onset_imp)) + geom_histogram(aes(y = ..density..),colour="black", fill="white") +geom_density(alpha=.2, fill="#FF6666")+facet_grid(sex ~ ., labeller = labeller(sex = sex.labs))+ggtitle('Figure 3:Distribution of illness onset')+xlab('Illness Onset') + ylab('Density')

case_phenotype_prs %>% 
  group_by(sex) %>% 
  summarize(mean = mean(ill_onset_imp, na.rm = T),
            sd = sd(ill_onset_imp, na.rm = T))

#ggplot(case_phenotype_prs, aes(x = quality_remissions)) + geom_histogram(aes(y =..density..),colour="black", fill="white") +geom_density(alpha=.2, fill="#FF6666")+facet_grid(sex ~ ., labeller = labeller(sex = sex.labs))+ggtitle('Figure 2:Distribution of the Quality of Remission')+xlab('Quality of Remission') + ylab('Density')

case_phenotype_prs %>% 
  group_by(sex) %>% 
  summarize(median = median(quality_remissions, na.rm = T))


#ggplot(case_phenotype_prs, aes(x = num_hosp)) + geom_histogram(aes(y = ..density..),colour="black", fill="white") +geom_density(alpha=.2, fill="#FF6666")+facet_grid(sex ~ ., labeller = labeller(sex = sex.labs))+ggtitle('Figure 1:Distribution of the number of hospitalization')+xlab('Number of Hospitalization') + ylab('Density')

case_phenotype_prs %>% 
  group_by(sex) %>% 
  summarize(mean = mean(num_hosp, na.rm = T),
            sd = sd(num_hosp, na.rm = T))



```

### create survival objects
```{r}

case_phenotype_prs$status <- 1

surv_object_illonset <- Surv(case_phenotype_prs$ill_onset_imp, case_phenotype_prs$status)
fit1 <- survfit(surv_object_illonset ~ 1, data = case_phenotype_prs)
ggsurvplot(fit1,data = case_phenotype_prs, pval = T)

#surv_object_first_hosp <- Surv(case_phenotype_prs$first_hosp, case_phenotype_prs$status)
#fit2 <- survfit(surv_object_first_hosp ~ 1, data = case_phenotype_prs)
#ggsurvplot(fit2,data = case_phenotype_prs, pval = T)

```


### change the classes of data
```{r}

library(MASS)

case_phenotype_prs$quality_remissions <- as.factor(case_phenotype_prs$quality_remissions)
case_phenotype_prs$place_of_birth_num <- as.factor(case_phenotype_prs$place_of_birth)

```

### regression analysis for PRS
```{r}
library(stringr)
```

#### results

### illness onset prs
```{r}
age_onset_prsmod <- list()
age_onset_prstable <- data.frame()
for(i in 1:8){
  predictors_covariables <- c('DSM4', 'sex','PC1', 'PC2' , 'PC3', 'PC4','PC5', 'PC6' , 'PC7', 'PC8','PC9','PC10')
  predictors_prs <- str_subset(colnames(case_phenotype_prs),'_0.05')[i:i]
  predictor <- predictors_prs %>% append(predictors_covariables) %>% na.omit()
  age_onset_prsmod[[i]] <- coxph(surv_object_illonset~., data = case_phenotype_prs[, c(predictor)]) 
  summary <- summary(age_onset_prsmod[[i]])
  age_onset_prstable <- data.frame(PRS=rownames(summary$conf.int)[1],'Parameter Estimate'= summary$coefficients[predictors_prs,'coef'],'P value'=summary$coefficients[predictors_prs,'Pr(>|z|)'], 'Hazard ratios' = summary$conf.int[predictors_prs,'exp(coef)'], 'HR CI lower' = summary$conf.int[predictors_prs, 'lower .95'], 'HR CI upper' = summary$conf.int[predictors_prs, 'upper .95']) %>% add_row(age_onset_prstable,.before = 1)
}

age_onset_prstable <- age_onset_prstable %>% mutate(PRS = str_replace(PRS,'SCZ_Pt_0.05', 'Schizophrenia'),PRS = str_replace(PRS,'BD_Pt_0.05', 'Bipolar Disorder'), PRS = str_replace(PRS,'MDD_Pt_0.05', 'Depression'), PRS = str_replace(PRS,'IQ_Pt_0.05', 'IQ'), PRS = str_replace(PRS,'EF_Pt_0.05', 'Executive Function'), PRS = str_replace(PRS,'CUD_Pt_0.05', 'Cannabis Use'), PRS = str_replace(PRS,'alcohol_Pt_0.05', 'Alcohol Dependence'),PRS = str_replace(PRS,'smoking_Pt_0.05', 'Smoking'))


age_onset_prstable <- age_onset_prstable %>% mutate(sign = case_when(P.value < 0.05 ~ 'Significant at p = 0.05', P.value > 0.05 ~ 'Not significant'))

#nothing passed correction

age_onset_prstable_word <- mutate_if(age_onset_prstable, is.numeric, round, digit = 3) 

age_onset_prstable_word <- flextable(age_onset_prstable_word, col_keys = c('PRS', 'Parameter.Estimate', 'HRCI', 'P.value')) %>% 
  compose(j = 'HRCI', value = as_paragraph(sprintf(Hazard.ratios,fmt = '%#.3f '), as_bracket(HR.CI.lower, HR.CI.upper))) %>% 
  add_header_lines('Table  9: Proband PRS and Illness Onset - EU') %>% 
  color(~ P.value < 0.001, ~ P.value, color = "red") %>% 
  set_header_labels(values = list(
  PRS = 'PGS',
  Parameter.Estimate = 'Parameter', 
  P.value = 'P value',
  HRCI = 'Hazard Ratio (95% CI)'
)) %>% set_table_properties(layout = "autofit") 

```



### Illness onset ntprs
```{r}
age_onset_ntprsmod <- list()
age_onset_ntprstable <- data.frame()
for(i in 1:8){
  predictors_covariables <- c('DSM4', 'sex','PC1', 'PC2' , 'PC3', 'PC4','PC5', 'PC6' , 'PC7', 'PC8','PC9','PC10')
  predictors_ntprs <- str_subset(colnames(case_phenotype_prs),'non_transmitted')[i:i]
  predictor <- predictors_ntprs %>% append(predictors_covariables) %>% na.omit()
  age_onset_ntprsmod[[i]] <- coxph(surv_object_illonset~., data = case_phenotype_prs[, c(predictor)]) 
  summary <- summary(age_onset_ntprsmod[[i]])
  age_onset_ntprstable <- data.frame(ntPRS=rownames(summary$conf.int)[1],'Parameter Estimate'= summary$coefficients[predictors_ntprs,'coef'],'P value'=summary$coefficients[predictors_ntprs,'Pr(>|z|)'], 'Hazard ratios' = summary$conf.int[predictors_ntprs,'exp(coef)'], 'HR CI lower' = summary$conf.int[predictors_ntprs, 'lower .95'], 'HR CI upper' = summary$conf.int[predictors_ntprs, 'upper .95']) %>% add_row(age_onset_ntprstable,.before = 1)
}

p.adjust(age_onset_ntprstable$'P.value', method='bonferroni', n = 24)

age_onset_ntprstable <- age_onset_ntprstable %>% mutate(ntPRS = str_replace(ntPRS,'non_transmitted_prs_scz', 'Schizophrenia'),ntPRS = str_replace(ntPRS,'non_transmitted_prs_bd', 'Bipolar Disorder'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_mdd', 'Depression'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_IQ', 'IQ'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_EF', 'Executive Function'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_cud', 'Cannabis Use'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_alcohol', 'Alcohol Dependence'),ntPRS = str_replace(ntPRS,'non_transmitted_prs_smoking', 'Smoking'))
 
age_onset_ntprstable <- age_onset_ntprstable %>% mutate(sign = case_when(P.value < 0.05 ~ 'Significant at p = 0.05', P.value > 0.05 ~ 'Not significant'))

#nothing passed
# definitely a trend between IQ and smoking and earier age onset


age_onset_ntprstable_word <- mutate_if(age_onset_ntprstable, is.numeric, round, digit = 3) 

age_onset_ntprstable_word <- flextable(age_onset_ntprstable_word, col_keys = c('ntPRS', 'Parameter.Estimate', 'HRCI', 'P.value')) %>% 
  compose(j = 'HRCI', value = as_paragraph(sprintf(Hazard.ratios,fmt = '%#.3f '), as_bracket(HR.CI.lower, HR.CI.upper))) %>% 
  add_header_lines('Table  10: Proband ntPRS and Illness Onset - EU') %>% 
  color(~ P.value < 0.001, ~ P.value, color = "red") %>% 
  set_header_labels(values = list(
  ntPRS = 'ntPGS',
  Parameter.Estimate = 'Parameter', 
  P.value = 'P value',
  HRCI = 'Hazard Ratio (95% CI)'
)) %>% set_table_properties(layout = "autofit") 
```

```{r}
age_onset_ntprstable
age_onset_prstable

colnames(age_onset_ntprstable)[1] <- 'PGS'
colnames(age_onset_prstable)[1] <- 'PGS'
age_onset_ntprstable$type <- 'ntPGS'
age_onset_prstable$type <- 'PGS'

test <- rbind(age_onset_prstable, age_onset_ntprstable)
test$type <- as.factor(test$type) %>% relevel('PGS')
test$PGS <- as.factor(test$PGS) %>% ordered(levels = rev(c('Schizophrenia',"Bipolar Disorder","Depression","IQ","Executive Function","Cannabis Use","Alcohol Dependence","Smoking")))


ggplot(test, aes(y = PGS, x = Hazard.ratios)) +
  geom_point(aes(color = sign),shape = 18, size = 5) +  
  scale_color_manual(values = c("black", 'pink'), name = '') + 
  geom_errorbarh(aes(xmin = HR.CI.lower, xmax = HR.CI.upper), height = 0.25) +
  geom_vline(xintercept = 1, color = "red", linetype = "dashed", cex = 1, alpha = 0.5) + facet_wrap(~type)+
  xlab("Hazard Ratio (95% CI)") + 
  ylab(" ") + theme_classic() +
  ggtitle('Figure 8: Polygenic Scores and non-transmitted PGS with Illness Onset - EU') +
  theme(plot.title = element_text(hjust = 0.7))

ggsave(filename = 'figure8_prs_ntprs_illness_onset-eu.tiff', units = 'in', width = 7.5, height = 5, dpi = 700, device = 'tiff')

table6 <- as_grouped_data(x = test, groups = c('type')) %>% flextable::as_flextable(col_keys = c('Genotype', 'HRCI', 'P.value'))%>% compose(j = 'Genotype',i= ~ is.na(type), value = as_paragraph(PGS)) %>% 
  compose(j = 'HRCI', i= ~ is.na(type), value = as_paragraph(sprintf(Hazard.ratios,fmt = '%#.3f '), as_bracket(HR.CI.lower, HR.CI.upper))) %>%
  compose(j = 'P.value', i= ~ is.na(type), value = as_paragraph(sprintf(P.value,fmt = '%#.3f ')))%>% 
  add_header_lines('Table  6: Proband PGS, ntPGS and Illness Onset - EU') %>% 
  color(~ P.value < 0.05, ~ P.value, color = "red") %>% 
  set_header_labels(values = list(
  P.value = 'P value',
  HRCI = 'Hazard Ratio (95% CI)'
)) %>% bold(j = 1, i = ~ !is.na(type), bold = TRUE, part = "body") %>%
  bold(part = "header", bold = TRUE)%>% set_table_properties(layout = "autofit")
table6 %>% save_as_docx(path = 'table6.docx')
table6 %>%save_as_image(path = 'table6.png')
```
### quality remission PRS
```{r}
quality_remission_prsmod <- list()
quality_remission_prstable <- data.frame()
for(i in 1:8){
  predictors_covariables <- c('DSM4', 'sex','PC1', 'PC2' , 'PC3', 'PC4','PC5', 'PC6' , 'PC7', 'PC8','PC9','PC10')
  predictors_prs <- str_subset(colnames(case_phenotype_prs),'_0.05')[i:i] %>% append(predictors_covariables) %>% na.omit()
  quality_remission_prsmod[[i]] <- polr(quality_remissions~.,data = case_phenotype_prs[, c('quality_remissions', predictors_prs)],Hess=T)
  table <- coef(summary(quality_remission_prsmod[[i]]))
  p <- pnorm(abs(table[, 't value']), lower.tail = F)*2
  table <- cbind(table, 'p value' = p) %>% as.data.frame()
  ci<- confint(quality_remission_prsmod[[i]])%>% as.data.frame()
  or_ci <- exp(cbind(OR = coef(quality_remission_prsmod[[i]]), ci)) %>% as.data.frame()
  table <- table[1,] %>% cbind(or_ci[1,]) 
  quality_remission_prstable <- data.frame(PRS=rownames(table), Coefficient = table$Value, Odds.Ratio = table$OR, OR_CI_lower = table$`2.5 %`, OR_CI_upper = table$`97.5 %`, pvalue=table$`p value`) %>% add_row(quality_remission_prstable,.before = 1)
}

library(brant)
library(regclass)
quality_remission_sc <- polr(quality_remissions ~., data = case_phenotype_prs[, c('quality_remissions', 'SCZ_Pt_0.05', predictors_covariables)],Hess=T)

brant(quality_remission_sc)

fit2 <- lm(as.numeric(quality_remissions)~., data = case_phenotype_prs[, c('quality_remissions', 'SCZ_Pt_0.05', predictors_covariables)])
regclass::VIF(fit2)


quality_remission_prstable <- quality_remission_prstable %>% mutate(sign = case_when(pvalue < 0.05 ~ 'Significant at p = 0.05', pvalue > 0.05 ~ 'Not significant'))

quality_remission_prstable<- quality_remission_prstable %>% mutate(PRS = str_replace(PRS,'SCZ_Pt_0.05', 'Schizophrenia'),PRS = str_replace(PRS,'BD_Pt_0.05', 'Bipolar Disorder'), PRS = str_replace(PRS,'MDD_Pt_0.05', 'Depression'), PRS = str_replace(PRS,'IQ_Pt_0.05', 'IQ'), PRS = str_replace(PRS,'EF_Pt_0.05', 'Executive Function'), PRS = str_replace(PRS,'CUD_Pt_0.05', 'Cannabis Use'), PRS = str_replace(PRS,'alcohol_Pt_0.05', 'Alcohol Dependence'),PRS = str_replace(PRS,'smoking_Pt_0.05', 'Smoking'))
                                                  
quality_remission_prstable_word <- mutate_if(quality_remission_prstable, is.numeric, round, digit = 3) 

quality_remission_prstable_word <- flextable(quality_remission_prstable_word, col_keys = c('PRS', 'Coefficient', 'OddRatioCL', 'pvalue')) %>% 
  compose(j = 'OddRatioCL', value = as_paragraph(sprintf(Odds.Ratio,fmt = '%#.3f '), as_bracket(OR_CI_lower, OR_CI_upper))) %>% 
  add_header_lines('Table  11: Proband PRS and Quality of Remission - EU') %>% 
  color(~ pvalue < 0.001, ~ pvalue, color = "red") %>% 
  set_header_labels(values = list(
  Coefficient = 'Coefficient',
  pvalue = 'P value',
  OddRatioCL = 'Odd Ratio (95% CI)')) %>% 
  set_table_properties(layout = "autofit") 

# nothing passed multiple comparision problems
```
### quality remission ntprs
```{r}


quality_remission_ntprsmod <- list()
quality_remission_ntprstable <- data.frame()

for(i in 1:8){
  predictors_covariables <- c('DSM4', 'sex', 'PC1', 'PC2' , 'PC3', 'PC4','PC5', 'PC6' , 'PC7', 'PC8','PC9','PC10')
  predictors_ntprs <- str_subset(colnames(case_phenotype_prs),'non_transmitted')[i:i] %>% append(predictors_covariables) %>% na.omit()
  quality_remission_ntprsmod[[i]] <- polr(quality_remissions~.,data = case_phenotype_prs[, c('quality_remissions', predictors_ntprs)],Hess=T)
  table <- coef(summary(quality_remission_ntprsmod[[i]]))
  p <- pnorm(abs(table[, 't value']), lower.tail = F)*2
  table <- cbind(table, 'p value' = p) %>% as.data.frame()
  ci<- confint(quality_remission_ntprsmod[[i]])%>% as.data.frame()
  or_ci <- exp(cbind(OR = coef(quality_remission_ntprsmod[[i]]), ci)) %>% as.data.frame()
  table <- table[1,] %>% cbind(or_ci[1,]) 
  quality_remission_ntprstable <- data.frame(ntPRS=rownames(table), Coefficient = table$Value, 'Odds Ratio' = table$OR,  OR_CI_lower = table$`2.5 %`, OR_CI_upper = table$`97.5 %`,pvalue=table$`p value`) %>% add_row(quality_remission_ntprstable,.before = 1)
}



quality_remission_ntprstable <- quality_remission_ntprstable %>% mutate(sign = case_when(pvalue < 0.05 ~ 'Significant at p = 0.05', pvalue > 0.05 ~ 'Not significant'))

#nothing passed
quality_remission_ntprstable <- quality_remission_ntprstable %>% mutate(ntPRS = str_replace(ntPRS,'non_transmitted_prs_scz', 'Schizophrenia'),ntPRS = str_replace(ntPRS,'non_transmitted_prs_bd', 'Bipolar Disorder'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_mdd', 'Depression'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_IQ', 'IQ'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_EF', 'Executive Function'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_cud', 'Cannabis Use'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_alcohol', 'Alcohol Dependence'),ntPRS = str_replace(ntPRS,'non_transmitted_prs_smoking', 'Smoking'))
                                                  
quality_remission_ntprstable_word <- mutate_if(quality_remission_ntprstable, is.numeric, round, digit = 3) 

quality_remission_ntprstable_word <- flextable(quality_remission_ntprstable_word, col_keys = c('ntPRS', 'Coefficient', 'OddRatioCL', 'pvalue')) %>% 
  compose(j = 'OddRatioCL', value = as_paragraph(sprintf(Odds.Ratio,fmt = '%#.3f '), as_bracket(OR_CI_lower, OR_CI_upper))) %>% 
  add_header_lines('Table  12: Proband ntPRS and Quality of Remission - EU') %>% 
  color(~ pvalue < 0.001, ~ pvalue, color = "red") %>% 
  set_header_labels(values = list(
    ntPRS = 'ntPGS',
  Coefficient = 'Coefficient',
  pvalue = 'P value',
  OddRatioCL = 'Odd Ratio (95% CI)')) %>% 
  set_table_properties(layout = "autofit") 
```

```{r}
quality_remission_prstable
quality_remission_ntprstable

quality_remission_ntprstable$type <- 'ntPGS'
quality_remission_prstable$type <- 'PGS'

colnames(quality_remission_prstable)[1] <- 'PGS'
colnames(quality_remission_ntprstable)[1] <- 'PGS'


test <- rbind(quality_remission_prstable, quality_remission_ntprstable)

test$type <- as.factor(test$type) %>% relevel('PGS')
test$PGS <- as.factor(test$PGS) %>% ordered(levels = rev(c('Schizophrenia',"Bipolar Disorder","Depression","IQ","Executive Function","Cannabis Use","Alcohol Dependence","Smoking")))


ggplot(test, aes(y = PGS, x = Odds.Ratio)) +
  geom_point(aes(color = sign),shape = 18, size = 5) +  
  scale_color_manual(values = c("black", 'pink'), name = '') + 
  geom_errorbarh(aes(xmin = OR_CI_lower, xmax = OR_CI_upper), height = 0.25) +
  geom_vline(xintercept = 1, color = "red", linetype = "dashed", cex = 1, alpha = 0.5) + facet_wrap(~type)+
  xlab("Odd Ratio (95% CI)") + 
  ylab(" ") + theme_classic() +
  ggtitle('Figure 9: Polygenic Scores and non-transmitted PGS with Quality of Remission - EU') +
  theme(plot.title = element_text(hjust = 0.5))

ggsave(filename = 'figure9_prs_ntprs_quality_remission-eu.tiff', units = 'in', width = 7.5, height = 5, dpi = 700, device = 'tiff')

table7 <- as_grouped_data(x = test, groups = c('type')) %>% flextable::as_flextable(col_keys = c('Genotype', 'ORCI', 'pvalue'))%>%compose(j = 'Genotype',i= ~ is.na(type), value = as_paragraph(PGS))%>% 
  compose(j = 'ORCI', i= ~ is.na(type), value = as_paragraph(sprintf(Odds.Ratio,fmt = '%#.3f '), as_bracket(OR_CI_lower, OR_CI_upper)))%>%
  compose(j = 'pvalue', i= ~ is.na(type), value = as_paragraph(sprintf(pvalue,fmt = '%#.3f '))) %>% 
  add_header_lines('Table  7: Proband PGS, ntPGS and Quality of Remission - EU') %>% 
  color(~ pvalue < 0.05, ~ pvalue, color = "red") %>% 
  set_header_labels(values = list(
  pvalue = 'P value',
  ORCI = 'Odd Ratio (95% CI)'
)) %>% bold(j = 1, i = ~ !is.na(type), bold = TRUE, part = "body") %>%
  bold(part = "header", bold = TRUE)%>% set_table_properties(layout = "autofit")
table7 %>% save_as_docx(path = 'table7.docx')
table7 %>%save_as_image(path = 'table7.png')

```

```{r}

bi_quality_remissions_SCZPGS_glm <- glm(binary_quality_remission ~ SCZ_Pt_0.05 +
                                          DSM4 + sex + PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10,data = case_phenotype_prs, family = binomial)
summary(bi_quality_remissions_SCZPGS_glm)

```


### number of hosp PRS
```{r}

num_hosp_prsmod <- list()
num_hosp_prstable <- data.frame()
for(i in 1:8){
  predictors_covariables <- c('DSM4', 'sex', 'age', 'Durations_of_illness','PC1', 'PC2' , 'PC3', 'PC4','PC5', 'PC6' , 'PC7', 'PC8','PC9','PC10')
  predictors_prs <- str_subset(colnames(case_phenotype_prs),'_0.05')[i:i] 
  predictors <- predictors_prs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_prsmod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_prsmod[[i]])
  confint <- confint(num_hosp_prsmod[[i]])
  num_hosp_prstable <- data.frame(PRS=rownames(summary$coefficients)[2], Estimate = summary$coefficients[predictors_prs,'Estimate'],RateRatio = exp(summary$coefficients[predictors_prs,'Estimate']), CI_lower = exp(confint[predictors_prs, '2.5 %']), CI_upper = exp(confint[predictors_prs, '97.5 %']), pvalue=summary$coefficients[predictors_prs,'Pr(>|z|)']) %>% add_row(num_hosp_prstable,.before = 1)
}
summary(num_hosp_prsmod[[2]])
#explantiohn use odd ratio to make esier interprettion


num_hosp_prstable <- num_hosp_prstable %>% mutate(sign = case_when(pvalue < 0.05 ~ 'Significant at p = 0.05', pvalue > 0.05 ~ 'Not significant'))

num_hosp_prstable<- num_hosp_prstable %>% mutate(PRS = str_replace(PRS,'SCZ_Pt_0.05', 'Schizophrenia'),PRS = str_replace(PRS,'BD_Pt_0.05', 'Bipolar Disorder'), PRS = str_replace(PRS,'MDD_Pt_0.05', 'Depression'), PRS = str_replace(PRS,'IQ_Pt_0.05', 'IQ'), PRS = str_replace(PRS,'EF_Pt_0.05', 'Executive Function'), PRS = str_replace(PRS,'CUD_Pt_0.05', 'Cannabis Use'), PRS = str_replace(PRS,'alcohol_Pt_0.05', 'Alcohol Dependence'),PRS = str_replace(PRS,'smoking_Pt_0.05', 'Smoking'))
                                                  
num_hosp_prstable_word <- mutate_if(num_hosp_prstable, is.numeric, round, digit = 3) 

num_hosp_prstable_word <- flextable(num_hosp_prstable_word, col_keys = c('PRS', 'Estimate', 'RateRatioCL', 'pvalue')) %>% 
  compose(j = 'RateRatioCL', value = as_paragraph(sprintf(RateRatio,fmt = '%#.3f '), as_bracket(CI_lower, CI_upper))) %>% 
  add_header_lines('Table  13: Proband PRS and Number of Hospitalization - EU') %>% 
  color(~ pvalue < 0.001, ~ pvalue, color = "red") %>% 
  set_header_labels(values = list(
  Estimate = 'Beta',
  pvalue = 'P value',
  RateRatioCL = 'Rate Ratio (95% CI)'
)) %>% 
  set_table_properties(layout = "autofit") 

# BD passed multiple comparision problems
#analysis for pTDT
pTDT_bd_for_num_hosp  <- glm.nb(num_hosp ~ pTDT_bd + DSM4 + sex + age + Durations_of_illness,data = case_phenotype_prs)

summary(pTDT_bd_for_num_hosp)



```

### number of hosp ntPRS
```{R}
num_hosp_ntprsmod <- list()
num_hosp_ntprstable <- data.frame()
for(i in 1:8){
  predictors_covariables <- c('DSM4', 'sex', 'age', 'Durations_of_illness','PC1', 'PC2' , 'PC3', 'PC4','PC5', 'PC6' , 'PC7', 'PC8','PC9','PC10')
  predictors_ntprs <- str_subset(colnames(case_phenotype_prs),'non_transmitted')[i:i] 
  predictors <- predictors_ntprs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_ntprsmod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_ntprsmod[[i]])
  confint <- confint(num_hosp_ntprsmod[[i]])
  num_hosp_ntprstable <- data.frame(ntPRS=rownames(summary$coefficients)[2],  Estimate = summary$coefficients[predictors_ntprs,'Estimate'], RateRatio = exp(summary$coefficients[predictors_ntprs,'Estimate']), CI_lower = exp(confint[predictors_ntprs, '2.5 %']), CI_upper = exp(confint[predictors_ntprs, '97.5 %']), pvalue =summary$coefficients[predictors_ntprs,'Pr(>|z|)']) %>% add_row(num_hosp_ntprstable,.before = 1)
}
p.adjust(num_hosp_ntprstable$'pvalue', method='bonferroni', n = 24)

num_hosp_ntprstable <- num_hosp_ntprstable %>% mutate(sign = case_when(pvalue < 0.05 ~ 'Significant at p = 0.05', pvalue > 0.05 ~ 'Not significant'))

#IQ, EF and Smoking passed the correction

num_hosp_ntprstable <- num_hosp_ntprstable %>% mutate(ntPRS = str_replace(ntPRS,'non_transmitted_prs_scz', 'Schizophrenia'),ntPRS = str_replace(ntPRS,'non_transmitted_prs_bd', 'Bipolar Disorder'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_mdd', 'Depression'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_IQ', 'IQ'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_EF', 'Executive Function'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_cud', 'Cannabis Use'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_alcohol', 'Alcohol Dependence'),ntPRS = str_replace(ntPRS,'non_transmitted_prs_smoking', 'Smoking'))

num_hosp_ntprstable_word <- mutate_if(num_hosp_ntprstable, is.numeric, round, digit = 3) 

num_hosp_ntprstable_word <- flextable(num_hosp_ntprstable_word, col_keys = c('ntPRS', 'Estimate', 'RateRatioCL', 'pvalue')) %>% 
  compose(j = 'RateRatioCL', value = as_paragraph(sprintf(RateRatio,fmt = '%#.3f '), as_bracket(CI_lower, CI_upper))) %>% 
  add_header_lines('Table  14: Proband ntPRS and Number of Hospitalization - EU') %>% 
  color(~ pvalue < 0.001, ~ pvalue, color = "red") %>% 
  set_header_labels(values = list(
  Estimate = 'Beta',
  ntPRS = 'ntPGS',
  pvalue = 'P value',
  RateRatioCL = 'Rate Ratio (95% CI)'
)) %>% set_table_properties(layout = "autofit") 
```

```{r}
num_hosp_prstable
num_hosp_ntprstable

num_hosp_prstable$type <- 'PGS'
num_hosp_ntprstable$type <- 'ntPGS'

colnames(num_hosp_prstable)[1] <- 'PGS'
colnames(num_hosp_ntprstable)[1] <- 'PGS'


test <- rbind(num_hosp_prstable, num_hosp_ntprstable)

test$type <- as.factor(test$type) %>% relevel('PGS')
test$PGS <- as.factor(test$PGS) %>% ordered(levels = rev(c('Schizophrenia',"Bipolar Disorder","Depression","IQ","Executive Function","Cannabis Use","Alcohol Dependence","Smoking")))


ggplot(test, aes(y = PGS, x = RateRatio)) +
  geom_point(aes(color = sign),shape = 18, size = 5) +  
  scale_color_manual(values = c("black", 'pink'), name = '') + 
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper), height = 0.25) +
  geom_vline(xintercept = 1, color = "red", linetype = "dashed", cex = 1, alpha = 0.5) + facet_wrap(~type)+
  xlab("Rate Ratio (95% CI)") + 
  ylab(" ") + theme_classic() +
  ggtitle('Figure 10: Polygenic Scores and non-transmitted PGS with number of hospitalizations - EU') +
  theme(plot.title = element_text(hjust = 0.4))

ggsave(filename = 'figure10_prs_ntprs_num_hosp-eu.tiff', units = 'in', width = 7.5, height = 5, dpi = 700, device = 'tiff')

table8 <- as_grouped_data(x = test, groups = c('type')) %>% flextable::as_flextable(col_keys = c('Genotype', 'RRCI', 'pvalue'))%>% 
  compose(j = 'RRCI', i= ~ is.na(type), value = as_paragraph(sprintf(RateRatio,fmt = '%#.3f '), as_bracket(CI_lower, CI_upper))) %>%compose(j = 'Genotype',i= ~ is.na(type), value = as_paragraph(PGS)) %>%
  compose(j = 'pvalue', i= ~ is.na(type), value = as_paragraph(sprintf(pvalue,fmt = '%#.3f '))) %>%
  add_header_lines('Table  8: Proband PGS, ntPGS and number of hospitalizations - EU') %>% 
  color(~ pvalue < 0.05, ~ pvalue, color = "red") %>% 
  set_header_labels(values = list(
  pvalue = 'P value',
  RRCI = 'Rate Ratio (95% CI)'
)) %>% bold(j = 1, i = ~ !is.na(type), bold = TRUE, part = "body") %>%
  compose(i = 18, j = 3, as_paragraph(as_chunk('< 0.001'))) %>%
  bold(part = "header", bold = TRUE)%>% set_table_properties(layout = "autofit")
table8 %>%save_as_image(path = 'table8.png')



```


```{r}
library(webshot)

```

```{R}
mother_prs_pc <- phenotype_pc_prs %>% 
  filter(IndividualID == 3) %>% 
  filter(!(FamilyID %in% excluding_family_id))

mother_prs_pc <- subset(mother_prs_pc, select = grepl(pattern = 'FamilyID|IQ_Pt_0.05|IndividualID|PC|smoking_Pt_0.05', names(mother_prs_pc))) %>% rename_with(~ paste0(.x, '_mother'))

mother_prs_pc$IndividualID_mother <- 1

mother_prs_pc$mergeID <- str_c(mother_prs_pc$FamilyID_mother, '-',mother_prs_pc$IndividualID_mother)

mother_prs_pc <- mother_prs_pc %>% subset(select=-c(FamilyID_mother, IndividualID_mother))

case_phenotype_prs <- left_join(case_phenotype_prs, mother_prs_pc, by = c('IID'='mergeID'))

father_prs_pc <- phenotype_pc_prs %>% 
  filter(IndividualID == 2) %>% 
  filter(!(FamilyID %in% excluding_family_id))

father_prs_pc <- subset(father_prs_pc, select = grepl(pattern = 'FamilyID|IQ_Pt_0.05|IndividualID|PC|smoking_Pt_0.05', names(father_prs_pc))) %>% rename_with(~ paste0(.x, '_father'))

father_prs_pc$IndividualID_father <- 1

father_prs_pc$mergeID <- str_c(father_prs_pc$FamilyID_father, '-',father_prs_pc$IndividualID_father)

father_prs_pc <- father_prs_pc %>% subset(select=-c(FamilyID_father, IndividualID_father))

case_phenotype_prs <- left_join(case_phenotype_prs, father_prs_pc, by = c('IID'='mergeID'))


num_hosp_parentprs_mod <- list()
num_hosp_parentprs_table <- data.frame()
for(i in c('IQ_Pt_0.05', 'smoking_Pt_0.05')){
  predictors_covariables <- c('DSM4', 'sex', 'age', 'Durations_of_illness', 'PC1', 'PC2' , 'PC3', 'PC4','PC5', 'PC6' , 'PC7', 'PC8','PC9','PC10')
  predictors_prs <- str_subset(colnames(case_phenotype_prs),i)
  predictors <- predictors_prs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_parentprs_mod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_parentprs_mod[[i]])
  confint <- confint(num_hosp_parentprs_mod[[i]])
  num_hosp_parentprs_table <- data.frame(Genotype = i, Estimate_proband=summary$coefficients[2,'Estimate'], pvalue_proband=summary$coefficients[2,'Pr(>|z|)'], CI_lower_proband = confint[2, '2.5 %'], CI_upper_proband = confint[2, '97.5 %'],Estimate_father = summary$coefficients[3,'Estimate'], pvalue_father=summary$coefficients[3,'Pr(>|z|)'], CI_lower_father = confint[3, '2.5 %'], CI_upper_father = confint[3, '97.5 %'], Estimate_mother = summary$coefficients[4,'Estimate'], pvalue_mother=summary$coefficients[4,'Pr(>|z|)'], CI_lower_mother = confint[4, '2.5 %'], CI_upper_mother = confint[4, '97.5 %']) %>% add_row(num_hosp_parentprs_table,.before = 1)
}

mutate_if(num_hosp_parentprs_table, is.numeric, round, digit = 3) %>% flextable() %>% add_header_lines('Appendix Table  1: Effects of Parents PGS when controlling for Proband PGS') %>% save_as_image(path = 'appendix.png')
```

#doing following up analysis...


```{r}
#mother effect


#IQ
num_hosp_motherprs_mod <- list()
num_hosp_motherprs_table <- data.frame()
for(i in 1:2){
  predictors_covariables <- c('DSM4', 'sex', 'age', 'Durations_of_illness','PC1_mother', 'PC2_mother' , 'PC3_mother', 'PC4_mother','PC5_mother', 'PC6_mother' , 'PC7_mother', 'PC8_mother','PC9_mother','PC10_mother')
  predictors_ntprs <- str_subset(colnames(case_phenotype_prs),'_0.05_mother')[i:i] 
  predictors <- predictors_ntprs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_motherprs_mod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_motherprs_mod[[i]])
  confint <- confint(num_hosp_motherprs_mod[[i]])
  num_hosp_motherprs_table <- data.frame(PRS=rownames(summary$coefficients)[2], Rate_Ratio_m =exp(summary$coefficients[predictors_ntprs,'Estimate']), CI_lower_m = exp(confint[predictors_ntprs, '2.5 %']), CI_upper_m = exp(confint[predictors_ntprs, '97.5 %']), pvalue_m=summary$coefficients[predictors_ntprs,'Pr(>|z|)']) %>% add_row(num_hosp_motherprs_table,.before = 1)
}

num_hosp_motherprs_table <- num_hosp_motherprs_table %>% 
  mutate(PRS = str_replace(PRS,'IQ_Pt_0.05_mother', 'IQ'),
         PRS = str_replace(PRS,'smoking_Pt_0.05_mother', 'Smoking'))
colnames(num_hosp_motherprs_table)[1] <- 'Maternal PGS'

num_hosp_motherprs_table_word <- mutate_if(num_hosp_motherprs_table, is.numeric, round, digit = 3) 


```


#father effect

```{r}



num_hosp_fatherprs_mod <- list()
num_hosp_fatherprs_table <- data.frame()
for(i in 1:2){
  predictors_covariables <- c('DSM4', 'sex', 'age', 'Durations_of_illness','PC1_father', 'PC2_father' , 'PC3_father', 'PC4_father','PC5_father', 'PC6_father' , 'PC7_father', 'PC8_father','PC9_father','PC10_father')
  predictors_ntprs <- str_subset(colnames(case_phenotype_prs),'0.05_father')[i:i] 
  predictors <- predictors_ntprs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_fatherprs_mod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_fatherprs_mod[[i]])
  confint <- confint(num_hosp_fatherprs_mod[[i]])
  num_hosp_fatherprs_table <- data.frame(PRS=rownames(summary$coefficients)[2], Rate_ratio_f = exp(summary$coefficients[predictors_ntprs,'Estimate']), CI_lower_f = exp(confint[predictors_ntprs, '2.5 %']), CI_upper_f = exp(confint[predictors_ntprs, '97.5 %']), pvalue_f=summary$coefficients[predictors_ntprs,'Pr(>|z|)']) %>% add_row(num_hosp_fatherprs_table,.before = 1)
}
 

num_hosp_fatherprs_table <- num_hosp_fatherprs_table %>% 
  mutate(PRS = str_replace(PRS,'IQ_Pt_0.05_father', 'IQ'),
         PRS = str_replace(PRS,'smoking_Pt_0.05_father', 'Smoking'))

colnames(num_hosp_fatherprs_table)[1] <- 'PGS'

num_hosp_fatherprs_table_word <- mutate_if(num_hosp_fatherprs_table, is.numeric, round, digit = 3)




test <- cbind(num_hosp_fatherprs_table,num_hosp_motherprs_table)

table12 <- flextable(test, col_keys = c('PGS', 'RRCI_f', 'pvalue_f', 'RRCI_m', 'pvalue_m'))%>% 
  compose(j = 'PGS',value = as_paragraph(PGS)) %>%
  compose(j = 'RRCI_f', value = as_paragraph(sprintf(Rate_ratio_f,fmt = '%#.3f '), as_bracket(CI_lower_f, CI_upper_f))) %>%
  compose(j = 'pvalue_f', value = as_paragraph(sprintf(pvalue_f,fmt = '%#.3f '))) %>%
  compose(j = 'RRCI_m', value = as_paragraph(sprintf(Rate_Ratio_m,fmt = '%#.3f '), as_bracket(CI_lower_m, CI_upper_m))) %>%
  compose(j = 'pvalue_m', value = as_paragraph(sprintf(pvalue_m,fmt = '%#.3f '))) %>%
  color(~ pvalue_f < 0.05, ~ pvalue_f, color = "red") %>% 
  set_header_labels(values = list(
  pvalue_m = 'P value',
  RRCI_m = 'Rate Ratio (95% CI)',
  pvalue_f = 'P value',
  RRCI_f = 'Rate Ratio (95% CI)'
)) %>%
  add_header_row(colwidths = c(1,2,2), values = c('','Paternal', 'Maternal'))%>%
  add_header_lines("Table  12: Paternal and Maternal PGS and probands' hospitalizations") %>% set_table_properties(layout = "autofit")

table12 %>%save_as_image(path = 'table12.png')
table12 %>%save_as_docx(path = 'table12.docx')
```

#### exploratory analysis - family history pathways

```{r}
num_hosp_family_history_mod <- list()
num_hosp_family_history_table <- data.frame()

for(i in c(5)){
  predictors_covariables <- c('DSM4', 'sex', 'age', 'Durations_of_illness', 'family_history', 'PC1', 'PC2' , 'PC3', 'PC4','PC5', 'PC6' , 'PC7', 'PC8','PC9','PC10')
  predictors_prs <- str_subset(colnames(case_phenotype_prs), 'IQ')[i]
  predictors <- predictors_prs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_family_history_mod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_family_history_mod[[i]])
  confint <- confint(num_hosp_family_history_mod[[i]])
  num_hosp_family_history_table <- data.frame(PRS = predictors_prs, OR_withfamilyhistory=exp(summary$coefficients[2,'Estimate']), CI_lower_withfamilyhistory = exp(confint[2, '2.5 %']), CI_upper_withfamilyhistory= exp(confint[2, '97.5 %']), pvalue_withfamilyhistory=summary$coefficients[2,'Pr(>|z|)']) %>% add_row(num_hosp_family_history_table,.before = 1)
}

for(i in c(7)){
  predictors_covariables <- c('DSM4', 'sex', 'age', 'Durations_of_illness', 'family_history', 'PC1_mother', 'PC2_mother' , 'PC3_mother', 'PC4_mother','PC5_mother', 'PC6_mother' , 'PC7_mother', 'PC8_mother','PC9_mother','PC10_mother')
  predictors_prs <- str_subset(colnames(case_phenotype_prs), 'IQ')[i]
  predictors <- predictors_prs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_family_history_mod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_family_history_mod[[i]])
  confint <- confint(num_hosp_family_history_mod[[i]])
  num_hosp_family_history_table <- data.frame(PRS = predictors_prs, OR_withfamilyhistory=exp(summary$coefficients[2,'Estimate']), CI_lower_withfamilyhistory = exp(confint[2, '2.5 %']), CI_upper_withfamilyhistory= exp(confint[2, '97.5 %']), pvalue_withfamilyhistory=summary$coefficients[2,'Pr(>|z|)']) %>% add_row(num_hosp_family_history_table,.before = 1)
}



for(i in c(5)){
  predictors_covariables <- c('DSM4', 'sex', 'age', 'Durations_of_illness', 'family_history', 'PC1', 'PC2' , 'PC3', 'PC4','PC5', 'PC6' , 'PC7', 'PC8','PC9','PC10')
  predictors_prs <- str_subset(colnames(case_phenotype_prs), 'smoking')[i]
  predictors <- predictors_prs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_family_history_mod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_family_history_mod[[i]])
  confint <- confint(num_hosp_family_history_mod[[i]])
  num_hosp_family_history_table <- data.frame(PRS = predictors_prs, OR_withfamilyhistory=exp(summary$coefficients[2,'Estimate']), CI_lower_withfamilyhistory = exp(confint[2, '2.5 %']), CI_upper_withfamilyhistory= exp(confint[2, '97.5 %']), pvalue_withfamilyhistory=summary$coefficients[2,'Pr(>|z|)']) %>% add_row(num_hosp_family_history_table,.before = 1)
}

for(i in c(8)){
  predictors_covariables <- c('DSM4', 'sex', 'age', 'Durations_of_illness', 'family_history', 'PC1_father', 'PC2_father' , 'PC3_father', 'PC4_father','PC5_father', 'PC6_father' , 'PC7_father', 'PC8_father','PC9_father','PC10_father')
  predictors_prs <- str_subset(colnames(case_phenotype_prs), 'smoking')[i]
  predictors <- predictors_prs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_family_history_mod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_family_history_mod[[i]])
  confint <- confint(num_hosp_family_history_mod[[i]])
  num_hosp_family_history_table <- data.frame(PRS = predictors_prs, OR_withfamilyhistory=exp(summary$coefficients[2,'Estimate']), CI_lower_withfamilyhistory = exp(confint[2, '2.5 %']), CI_upper_withfamilyhistory= exp(confint[2, '97.5 %']), pvalue_withfamilyhistory=summary$coefficients[2,'Pr(>|z|)']) %>% add_row(num_hosp_family_history_table,.before = 1)
}



num_hosp_family_history_table <- num_hosp_family_history_table %>% 
  mutate(PRS = str_replace(PRS,'IQ_Pt_0.05_mother', 'Maternal IQ PGS'),
         PRS = str_replace(PRS,'EF_Pt_0.05_mother', 'Maternal EF PGS'), 
         PRS = str_replace(PRS,'smoking_Pt_0.05_father', 'Paternal Smoking PGS'),
         PRS = str_replace(PRS,'non_transmitted_prs_IQ', 'IQ ntPGS'),
         PRS = str_replace(PRS,'non_transmitted_prs_EF', 'EF ntPGS'),
         PRS = str_replace(PRS,'non_transmitted_prs_smoking', 'Smoking ntPGS'),
         PRS = str_replace(PRS,'non_transmitted_prs_alcohol', 'Alcohol ntPGS'),
         PRS = str_replace(PRS,'alcohol_Pt_0.05_mother', 'Maternal Alcohol PGS')
         )

colnames(num_hosp_family_history_table) <- c('ntPGS and Parental PGS', 'OR', 'CI_lower', 'CI_upper', 'pvalue')

num_hosp_family_history_table_word <- mutate_if(num_hosp_family_history_table, is.numeric, round, digit = 3) 

table13 <- flextable(num_hosp_family_history_table_word, col_keys = c('ntPGS and Parental PGS', 'RateRatioCL', 'pvalue')) %>% 
  compose(j = 'RateRatioCL', value = as_paragraph(sprintf(OR,fmt = '%#.3f '), as_bracket(CI_lower, CI_upper))) %>% 
  add_header_lines('Table  13: ntPGS, parental PRS, and Number of Hospitalization accounting for family history') %>% 
  color(~ pvalue < 0.05, ~ pvalue, color = "red") %>% 
  set_header_labels(values = list(
  pvalue = 'P value',
  RateRatioCL = 'Rate Ratio (95% CI)')) %>%
  set_table_properties(layout = "autofit") 
table13 %>% save_as_image(path = 'table13.png')
table13 %>% save_as_docx(path = 'table13.docx')
#save_as_image(num_hosp_family_history_table_word,path = 'table17.png')

age_onset_ntprsmod_familyhistory <- list()
age_onset_ntprstable_familyhistory <- data.frame()
for(i in 1:8){
  predictors_covariables <- c('DSM4', 'sex','parent_psychosis','PC1', 'PC2' , 'PC3', 'PC4','PC5', 'PC6' , 'PC7', 'PC8','PC9','PC10')
  predictors_ntprs <- str_subset(colnames(case_phenotype_prs),'non_transmitted')[i:i]
  predictor <- predictors_ntprs %>% append(predictors_covariables) %>% na.omit()
  age_onset_ntprsmod_familyhistory[[i]] <- coxph(surv_object_illonset~., data = case_phenotype_prs[, c(predictor)]) 
  summary <- summary(age_onset_ntprsmod_familyhistory[[i]])
  age_onset_ntprstable_familyhistory <- data.frame(ntPRS=rownames(summary$conf.int)[1],'Parameter Estimate'= summary$coefficients[predictors_ntprs,'coef'],'P value'=summary$coefficients[predictors_ntprs,'Pr(>|z|)'], 'Hazard ratios' = summary$conf.int[predictors_ntprs,'exp(coef)'], 'HR CI lower' = summary$conf.int[predictors_ntprs, 'lower .95'], 'HR CI upper' = summary$conf.int[predictors_ntprs, 'upper .95']) %>% add_row(age_onset_ntprstable_familyhistory,.before = 1)
}
```

```{r}
save_as_docx(age_onset_prstable_word,age_onset_ntprstable_word,
             quality_remission_prstable_word,quality_remission_ntprstable_word,
             num_hosp_prstable_word,num_hosp_ntprstable_word, 
             num_hosp_motherprs_table, num_hosp_fatherprs_table,
             num_hosp_family_history_table_word,
             path = 'dissertation table2.docx')

```

#### Number of hosp < 20 sample 
```{r}

case_phenotype_prs <- case_phenotype_prs %>% mutate(num_hosp = replace(num_hosp, which(num_hosp>20), NA))

ggplot(case_phenotype_prs, aes(x = num_hosp)) + geom_histogram(aes(y = ..density..),colour="black", fill="white") +geom_density(alpha=.2, fill="#FF6666")+facet_grid(sex ~ .)
table(case_phenotype_prs$num_hosp)

#library(AER)
df1 = glm(num_hosp ~ DSM4 + sex+ age+ Durations_of_illness+PC1+ PC2 + PC3+ PC4+PC5+ PC6 + PC7+ PC8+PC9+PC10 + BD_Pt_0.05 ,family=poisson, data = case_phenotype_prs)
dp = sum(residuals(df1, type="pearson")^2)/df1$df.residual 
dp
#summary(df1, dispersion=dp)

num_hosp_prsmod <- list()
num_hosp_prstable <- data.frame()
for(i in 1:8){
  predictors_covariables <- c('DSM4', 'sex', 'age', 'Durations_of_illness','PC1', 'PC2' , 'PC3', 'PC4','PC5', 'PC6' , 'PC7', 'PC8','PC9','PC10')
  predictors_prs <- str_subset(colnames(case_phenotype_prs),'_0.05')[i:i] 
  predictors <- predictors_prs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_prsmod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_prsmod[[i]])
  confint <- confint(num_hosp_prsmod[[i]])
  num_hosp_prstable <- data.frame(PRS=rownames(summary$coefficients)[2], Estimate = summary$coefficients[predictors_prs,'Estimate'],RateRatio = exp(summary$coefficients[predictors_prs,'Estimate']), CI_lower = exp(confint[predictors_prs, '2.5 %']), CI_upper = exp(confint[predictors_prs, '97.5 %']), pvalue=summary$coefficients[predictors_prs,'Pr(>|z|)']) %>% add_row(num_hosp_prstable,.before = 1)
}


num_hosp_prstable <- num_hosp_prstable %>% mutate(sign = case_when(pvalue < 0.05 ~ 'Significant at p = 0.05', pvalue > 0.05 ~ 'Not significant'))

num_hosp_prstable<- num_hosp_prstable %>% mutate(PRS = str_replace(PRS,'SCZ_Pt_0.05', 'Schizophrenia'),PRS = str_replace(PRS,'BD_Pt_0.05', 'Bipolar Disorder'), PRS = str_replace(PRS,'MDD_Pt_0.05', 'Depression'), PRS = str_replace(PRS,'IQ_Pt_0.05', 'IQ'), PRS = str_replace(PRS,'EF_Pt_0.05', 'Executive Function'), PRS = str_replace(PRS,'CUD_Pt_0.05', 'Cannabis Use'), PRS = str_replace(PRS,'alcohol_Pt_0.05', 'Alcohol Dependence'),PRS = str_replace(PRS,'smoking_Pt_0.05', 'Smoking'))
                                                  
num_hosp_prstable_word <- mutate_if(num_hosp_prstable, is.numeric, round, digit = 3) 

num_hosp_prstable_word <- flextable(num_hosp_prstable_word, col_keys = c('PRS', 'Estimate', 'RateRatioCL', 'pvalue')) %>% 
  compose(j = 'RateRatioCL', value = as_paragraph(sprintf(RateRatio,fmt = '%#.3f '), as_bracket(CI_lower, CI_upper))) %>% 
  add_header_lines('Table  18: Proband PGS and Number of Hospitalization (<20)') %>% 
  color(~ pvalue < 0.001, ~ pvalue, color = "red") %>% 
  set_header_labels(values = list(
    PRS = 'PGS',
  pvalue = 'P value',
  RateRatioCL = 'Rate Ratio (95% CI)'
)) %>% 
  set_table_properties(layout = "autofit") 

save_as_image(num_hosp_prstable_word,path = 'table18.png')

# BD passed multiple comparision problems
#analysis for pTDT
#pTDT_bd_for_num_hosp  <- glm(num_hosp ~ pTDT_bd + DSM4 + sex + age + #Durations_of_illness,data = case_phenotype_prs, family = poisson)

#summary(pTDT_bd_for_num_hosp)

#confint(pTDT_bd_for_num_hosp)



```

### number of hosp ntPRS
```{R}
num_hosp_ntprsmod <- list()
num_hosp_ntprstable <- data.frame()
for(i in 1:8){
  predictors_covariables <- c('DSM4', 'sex', 'age', 'Durations_of_illness','PC1', 'PC2' , 'PC3', 'PC4','PC5', 'PC6' , 'PC7', 'PC8','PC9','PC10')
  predictors_ntprs <- str_subset(colnames(case_phenotype_prs),'non_transmitted')[i:i] 
  predictors <- predictors_ntprs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_ntprsmod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_ntprsmod[[i]])
  confint <- confint(num_hosp_ntprsmod[[i]])
  num_hosp_ntprstable <- data.frame(ntPRS=rownames(summary$coefficients)[2],  Estimate = summary$coefficients[predictors_ntprs,'Estimate'], RateRatio = exp(summary$coefficients[predictors_ntprs,'Estimate']), CI_lower = exp(confint[predictors_ntprs, '2.5 %']), CI_upper = exp(confint[predictors_ntprs, '97.5 %']), pvalue =summary$coefficients[predictors_ntprs,'Pr(>|z|)']) %>% add_row(num_hosp_ntprstable,.before = 1)
}

num_hosp_ntprstable <- num_hosp_ntprstable %>% mutate(sign = case_when(pvalue < 0.05 ~ 'Significant at p = 0.05', pvalue > 0.05 ~ 'Not significant'))

#IQ, EF and Smoking passed the correction

num_hosp_ntprstable <- num_hosp_ntprstable %>% mutate(ntPRS = str_replace(ntPRS,'non_transmitted_prs_scz', 'Schizophrenia'),ntPRS = str_replace(ntPRS,'non_transmitted_prs_bd', 'Bipolar Disorder'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_mdd', 'Depression'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_IQ', 'IQ'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_EF', 'Executive Function'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_cud', 'Cannabis Use'), ntPRS = str_replace(ntPRS,'non_transmitted_prs_alcohol', 'Alcohol Dependence'),ntPRS = str_replace(ntPRS,'non_transmitted_prs_smoking', 'Smoking'))

num_hosp_ntprstable_word <- mutate_if(num_hosp_ntprstable, is.numeric, round, digit = 3) 

num_hosp_ntprstable_word <- flextable(num_hosp_ntprstable_word, col_keys = c('ntPRS', 'Estimate', 'RateRatioCL', 'pvalue')) %>% 
  compose(j = 'RateRatioCL', value = as_paragraph(sprintf(RateRatio,fmt = '%#.3f '), as_bracket(CI_lower, CI_upper))) %>% 
  add_header_lines('Table  19: Proband ntPGS and Number of Hospitalization (<20)') %>% 
  color(~ pvalue < 0.001, ~ pvalue, color = "red") %>% 
  set_header_labels(values = list(
  ntPRS = 'ntPGS',
  pvalue = 'P value',
  RateRatioCL = 'Rate Ratio (95% CI)'
)) %>% set_table_properties(layout = "autofit") 
save_as_image(num_hosp_ntprstable_word,path = 'table19.png')
```

```{r}
num_hosp_prstable
num_hosp_ntprstable

num_hosp_prstable$type <- 'PGS'
num_hosp_ntprstable$type <- 'ntPGS'

colnames(num_hosp_prstable)[1] <- 'PGS'
colnames(num_hosp_ntprstable)[1] <- 'PGS'


test <- rbind(num_hosp_prstable, num_hosp_ntprstable)

test$type <- as.factor(test$type) %>% relevel('PGS')
test$PGS <- as.factor(test$PGS) %>% ordered(levels = rev(c('Schizophrenia',"Bipolar Disorder","Depression","IQ","Executive Function","Cannabis Use","Alcohol Dependence","Smoking")))


ggplot(test, aes(y = PGS, x = RateRatio)) +
  geom_point(aes(color = sign),shape = 18, size = 5) +  
  scale_color_manual(values = c("black", 'pink'), name = '') + 
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper), height = 0.25) +
  geom_vline(xintercept = 1, color = "red", linetype = "dashed", cex = 1, alpha = 0.5) + facet_wrap(~type)+
  xlab("Rate Ratio (95% CI)") + 
  ylab(" ") + theme_classic() +
  ggtitle('Figure 11: Polygenic Scores and non-transmitted PGS with number of hospitalizations < 20') +
  theme(plot.title = element_text(hjust = 0.4, size = 10))

ggsave(filename = 'figure11_prs_ntprs_num_hosp_less_20.tiff', units = 'in', width = 7.5, height = 5, dpi = 700, device = 'tiff')

table9 <- as_grouped_data(x = test, groups = c('type')) %>% flextable::as_flextable(col_keys = c('Genotype', 'RRCI', 'pvalue'))%>% 
  compose(j = 'RRCI', i= ~ is.na(type), value = as_paragraph(sprintf(RateRatio,fmt = '%#.3f '), as_bracket(CI_lower, CI_upper))) %>%compose(j = 'Genotype',i= ~ is.na(type), value = as_paragraph(PGS)) %>%
  compose(j = 'pvalue', i= ~ is.na(type), value = as_paragraph(sprintf(pvalue,fmt = '%#.3f '))) %>%
  add_header_lines('Table  9: Proband PGS, ntPGS and number of hospitalizations < 20') %>% 
  color(~ pvalue < 0.05, ~ pvalue, color = "red") %>% 
  set_header_labels(values = list(
  pvalue = 'P value',
  RRCI = 'Rate Ratio (95% CI)'
)) %>% bold(j = 1, i = ~ !is.na(type), bold = TRUE, part = "body") %>%
  bold(part = "header", bold = TRUE)%>% set_table_properties(layout = "autofit")

table9 %>%save_as_image(path = 'table9.png')

```

#father effect

```{r}

num_hosp_fatherprs_mod <- list()
num_hosp_fatherprs_table <- data.frame()
for(i in 1:1){
  predictors_covariables <- c('DSM4', 'sex', 'age', 'Durations_of_illness','PC1_father', 'PC2_father' , 'PC3_father', 'PC4_father','PC5_father', 'PC6_father' , 'PC7_father', 'PC8_father','PC9_father','PC10_father')
  predictors_ntprs <- str_subset(colnames(case_phenotype_prs),'smoking_Pt_0.05_father')[i] 
  predictors <- predictors_ntprs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_fatherprs_mod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_fatherprs_mod[[i]])
  confint <- confint(num_hosp_fatherprs_mod[[i]])
  num_hosp_fatherprs_table <- data.frame(PRS=rownames(summary$coefficients)[2], Rate_ratio = exp(summary$coefficients[predictors_ntprs,'Estimate']), CI_lower = exp(confint[predictors_ntprs, '2.5 %']), CI_upper = exp(confint[predictors_ntprs, '97.5 %']), pvalue=summary$coefficients[predictors_ntprs,'Pr(>|z|)']) %>% add_row(num_hosp_fatherprs_table,.before = 1)
}
 

num_hosp_fatherprs_table <- num_hosp_fatherprs_table %>% 
  mutate(PRS = str_replace(PRS,'smoking_Pt_0.05_father', 'Smoking'))

colnames(num_hosp_fatherprs_table)[1] <- 'Paternal PGS'

num_hosp_fatherprs_table_word <- mutate_if(num_hosp_fatherprs_table, is.numeric, round, digit = 3)

num_hosp_fatherprs_table_word <- flextable(num_hosp_fatherprs_table_word, col_keys = c('Paternal PGS', 'RateRatioCL', 'pvalue')) %>% 
  compose(j = 'RateRatioCL', value = as_paragraph(sprintf(Rate_ratio,fmt = '%#.3f '), as_bracket(CI_lower, CI_upper))) %>% 
  add_header_lines('Table  x: Paternal PRS and Number of Hospitalization < 20') %>% 
  color(~ pvalue < 0.001, ~ pvalue, color = "red") %>% 
  set_header_labels(values = list(
  pvalue = 'P value',
  RateRatioCL = 'Rate Ratio (95% CI)')) %>%
  set_table_properties(layout = "autofit") 

num_hosp_fatherprs_table_word
```

#### exploratory analysis - family history pathways

```{r}
num_hosp_family_history_mod <- list()
num_hosp_family_history_table <- data.frame()

for(i in c(5)){
  predictors_covariables <- c('DSM4', 'sex', 'age', 'Durations_of_illness', 'family_history', 'PC1', 'PC2' , 'PC3', 'PC4','PC5', 'PC6' , 'PC7', 'PC8','PC9','PC10')
  predictors_prs <- str_subset(colnames(case_phenotype_prs), 'IQ')[i]
  predictors <- predictors_prs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_family_history_mod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_family_history_mod[[i]])
  confint <- confint(num_hosp_family_history_mod[[i]])
  num_hosp_family_history_table <- data.frame(PRS = predictors_prs, OR_withfamilyhistory=exp(summary$coefficients[2,'Estimate']), CI_lower_withfamilyhistory = exp(confint[2, '2.5 %']), CI_upper_withfamilyhistory= exp(confint[2, '97.5 %']), pvalue_withfamilyhistory=summary$coefficients[2,'Pr(>|z|)']) %>% add_row(num_hosp_family_history_table,.before = 1)
}

for(i in c(7)){
  predictors_covariables <- c('DSM4', 'sex', 'age', 'Durations_of_illness', 'family_history', 'PC1_mother', 'PC2_mother' , 'PC3_mother', 'PC4_mother','PC5_mother', 'PC6_mother' , 'PC7_mother', 'PC8_mother','PC9_mother','PC10_mother')
  predictors_prs <- str_subset(colnames(case_phenotype_prs), 'IQ')[i]
  predictors <- predictors_prs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_family_history_mod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_family_history_mod[[i]])
  confint <- confint(num_hosp_family_history_mod[[i]])
  num_hosp_family_history_table <- data.frame(PRS = predictors_prs, OR_withfamilyhistory=exp(summary$coefficients[2,'Estimate']), CI_lower_withfamilyhistory = exp(confint[2, '2.5 %']), CI_upper_withfamilyhistory= exp(confint[2, '97.5 %']), pvalue_withfamilyhistory=summary$coefficients[2,'Pr(>|z|)']) %>% add_row(num_hosp_family_history_table,.before = 1)
}



for(i in c(5)){
  predictors_covariables <- c('DSM4', 'sex', 'age', 'Durations_of_illness', 'family_history', 'PC1', 'PC2' , 'PC3', 'PC4','PC5', 'PC6' , 'PC7', 'PC8','PC9','PC10')
  predictors_prs <- str_subset(colnames(case_phenotype_prs), 'smoking')[i]
  predictors <- predictors_prs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_family_history_mod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_family_history_mod[[i]])
  confint <- confint(num_hosp_family_history_mod[[i]])
  num_hosp_family_history_table <- data.frame(PRS = predictors_prs, OR_withfamilyhistory=exp(summary$coefficients[2,'Estimate']), CI_lower_withfamilyhistory = exp(confint[2, '2.5 %']), CI_upper_withfamilyhistory= exp(confint[2, '97.5 %']), pvalue_withfamilyhistory=summary$coefficients[2,'Pr(>|z|)']) %>% add_row(num_hosp_family_history_table,.before = 1)
}

for(i in c(8)){
  predictors_covariables <- c('DSM4', 'sex', 'age', 'Durations_of_illness', 'family_history', 'PC1_father', 'PC2_father' , 'PC3_father', 'PC4_father','PC5_father', 'PC6_father' , 'PC7_father', 'PC8_father','PC9_father','PC10_father')
  predictors_prs <- str_subset(colnames(case_phenotype_prs), 'smoking')[i]
  predictors <- predictors_prs %>% append(predictors_covariables) %>% na.omit()
  num_hosp_family_history_mod[[i]] <- glm.nb(num_hosp~.,data = case_phenotype_prs[, c('num_hosp', predictors)])
  summary <- summary(num_hosp_family_history_mod[[i]])
  confint <- confint(num_hosp_family_history_mod[[i]])
  num_hosp_family_history_table <- data.frame(PRS = predictors_prs, OR_withfamilyhistory=exp(summary$coefficients[2,'Estimate']), CI_lower_withfamilyhistory = exp(confint[2, '2.5 %']), CI_upper_withfamilyhistory= exp(confint[2, '97.5 %']), pvalue_withfamilyhistory=summary$coefficients[2,'Pr(>|z|)']) %>% add_row(num_hosp_family_history_table,.before = 1)
}


num_hosp_family_history_table <- num_hosp_family_history_table %>% 
  mutate(PRS = str_replace(PRS,'IQ_Pt_0.05_mother', 'Maternal IQ PGS'),
         PRS = str_replace(PRS,'EF_Pt_0.05_mother', 'Maternal EF PGS'), 
         PRS = str_replace(PRS,'smoking_Pt_0.05_father', 'Paternal Smoking PGS'),
         PRS = str_replace(PRS,'non_transmitted_prs_IQ', 'IQ ntPGS'),
         PRS = str_replace(PRS,'non_transmitted_prs_EF', 'EF ntPGS'),
         PRS = str_replace(PRS,'non_transmitted_prs_smoking', 'Smoking ntPGS'),
         PRS = str_replace(PRS,'non_transmitted_prs_alcohol', 'Alcohol ntPGS'),
         PRS = str_replace(PRS,'alcohol_Pt_0.05_mother', 'Maternal Alcohol PGS')
         )

colnames(num_hosp_family_history_table) <- c('ntPGS and Parental PGS', 'OR', 'CI_lower', 'CI_upper', 'pvalue')

num_hosp_family_history_table_word <- mutate_if(num_hosp_family_history_table, is.numeric, round, digit = 3) 

num_hosp_family_history_table_word <- flextable(num_hosp_family_history_table_word, col_keys = c('ntPGS and Parental PGS', 'RateRatioCL', 'pvalue')) %>% 
  compose(j = 'RateRatioCL', value = as_paragraph(sprintf(OR,fmt = '%#.3f '), as_bracket(CI_lower, CI_upper))) %>% 
  add_header_lines('Table  17: ntPGS, parental PRS, and Number of Hospitalization accounting for family history') %>% 
  color(~ pvalue < 0.001, ~ pvalue, color = "red") %>% 
  set_header_labels(values = list(
  pvalue = 'P value',
  RateRatioCL = 'Rate Ratio (95% CI)')) %>%
  set_table_properties(layout = "autofit") 

num_hosp_family_history_table_word
```


```{r}

gwas_table <- read_csv(file = 'gwas_table.csv')

gwas_table <- flextable(gwas_table) %>% add_header_lines('Table 2: Summary of Genome-Wide Association Studies') %>% add_footer_row(value = '*Diagnosis according to international consensus criteria including DSM-4, DSM-5, ICD-9 or ICD-10',colwidths = 5)%>%
  set_table_properties(layout = "autofit")

save_as_image(gwas_table,path = 'gwas_sumamry.png')
save_as_docx(gwas_table, path = 'gwas summary.docx')
library(officer)
sect_properties <- prop_section(
  page_size = page_size(
    width = 20, height = 100
  ),
  type = "nextPage",
  page_margins = page_mar()
)
save_as_docx(table3, table4,table5, table6, table7, table8,table9,table10,table11,table12,table13,table14,table15,path = 'table.docx',pr_section = sect_properties)
```